Compiling refinement types to dependent types

### 2020-07-07 tex/paper.tex
Core language doesn't have any intrinsic equality

$\mu_\tau$ is defined as follows:
\begin{equation}
\begin{aligned}
  & \mu_\tau( (x : \nonterm{ts}_1) \rightarrow \nonterm{ts}_2)  && \triangleq \Pi x : \mu_\tau(\nonterm{ts}_1). \mu_\tau(\nonterm{ts}_2)        \\
  & \mu_\tau( \{ v : \nonterm{ts} | \nonterm{r} \})             && \triangleq \{ v : \mu_\tau(\nonterm{ts})\ **\ \mu_\tau(\nonterm r) \}        \\
  & \mu_\tau( \nonterm r_1 \land \nonterm r_2 )                 && \triangleq ( \mu_\tau(\nonterm r_1) , \mu_\tau(\nonterm r_2))                \\
  & \mu_\tau( \nonterm{es}_1 = \nonterm{es}_2 )                 && \triangleq \mu_\varepsilon(\nonterm{es}_1) = \mu_\varepsilon(\nonterm{es}_2) \\
%TODO add syntax/typing rules for True
  & \mu_\tau(B)                                                 && \triangleq B                                                                 \\
\end{aligned}
\end{equation}
Or, in words:
\begin{itemize}
  \item (dependent) arrow types are translated to the corresponding $\Pi$-types,
  \item refined types are translated to the corresponding $\Sigma$-types,
  \item atomic refinements, being propositions about surface language terms equality,
    are translated to propositions stating the equality of translated core language terms,
  \item conjunctions of several (atomic) refinements are represented as tuples of the corresponding atomic translations.
\end{itemize}

>>>>

$\mu_\tau$ is defined as follows:
\begin{equation}
\begin{aligned}
  & \mu_\tau( (x : \nonterm{ts}_1) \rightarrow \nonterm{ts}_2)  && \triangleq \Pi x : \mu_\tau(\nonterm{ts}_1). \mu_\tau(\nonterm{ts}_2)              \\
  & \mu_\tau( \{ v : \nonterm{ts} | \nonterm{r} \})             && \triangleq \{ v : \mu_\tau(\nonterm{ts})\ **\ \mu_\tau(\nonterm r) \}              \\
  & \mu_\tau( \nonterm r_1 \land \nonterm r_2 )                 && \triangleq ( \mu_\tau(\nonterm r_1) , \mu_\tau(\nonterm r_2))                      \\
  & \mu_\tau( \nonterm{es}_1 = \nonterm{es}_2 )                 && \triangleq \mu_\varepsilon(\nonterm{es}_1) \equiv \mu_\varepsilon(\nonterm{es}_2)  \\
%TODO add syntax/typing rules for True
  & \mu_\tau(B)                                                 && \triangleq B                                                                       \\
\end{aligned}
\end{equation}
Or, in words:
\begin{itemize}
  \item (dependent) arrow types are translated to the corresponding $\Pi$-types,
  \item refined types are translated to the corresponding $\Sigma$-types,
  \item atomic refinements, being propositions about surface language terms equality,
    are translated to propositions stating the equality of translated core language terms,
  \item conjunctions of several (atomic) refinements are represented as tuples of the corresponding atomic translations.
\end{itemize}
